>

### 2020-05-13 manuscript/appendix.Rmd
Rebuild appendix tables with accessibility measures all on one line
Addresses #7

```{r}
pa_models <- read_rds(here("data/pa_models.rds"))
pa_models$Tweets <- NULL
obesity_models <- read_rds(here("data/obesity_models.rds"))
obesity_models$Tweets <- NULL
```

@@

names_for_terms <- c(
  base_termnames, str_c("$\\gamma$: ", base_termnames[-1])
)

lambda <- "$\\lambda$: spatial correlation"
access_terms <- c("Size and Distance", "Attributes", "10-min walk")

ob_names <- c(base_termnames, "Physical Activity Rate")
ob_names <- c(
  ob_names, str_c("$\\gamma$: ", ob_names[-1])
)

```

\begin{table*}
  \caption{\label{tab:pa-fullmodels} Estimated Effect of Accessibility on Physical Activity Rates}
  \begin{center}
  \scalebox{0.7}{
```{r pa-fullmodels, results = "asis"}
texreg(pa_models, digits = 4, ci.force = TRUE,
       booktabs = TRUE, use.packages = FALSE, 
       custom.coef.names = c(names_for_terms, lambda, access_terms),
       custom.model.names = c("No Access", access_terms), table = F,
       caption.above = TRUE, include.aic = F, include.lr = F,
       custom.note = "%stars 95\\% confidence interval in brackets.")
```
}\end{center}
\end{table*}

\begin{table*}
  \caption{\label{tab:ob-fullmodels} Estimated Effect of Accessibility on Obesity Rates}
  \begin{center}
  \scalebox{0.7}{
```{r ob-fullmodels, results="asis"}
texreg(obesity_models, digits = 4, ci.force = TRUE,
       booktabs = TRUE, use.packages = FALSE, 
       custom.coef.names = c(ob_names, lambda, access_terms),
       custom.model.names = c("No Access", access_terms), table = F,
       caption.above = TRUE, include.aic = F, include.lr = F, 
       custom.note = "%stars 95\\% confidence interval in brackets.")
```
}\end{center}
\end{table*}

>>>>

```{r}
pa_models <- read_rds(here("data/pa_models.rds"))
obesity_models <- read_rds(here("data/obesity_models.rds"))
```

@@

cmnames <- c(
  base_termnames, str_c("$\\gamma$: ", base_termnames[-1]), 
  rep("Accessibility", 3), "$\\lambda$: spatial correlation"
)

#coefficient map
cm <- as.list(cmnames)
names(cm) <- c(names(pa_models$Logsum$coefficients), "euc_multi", "walk10TRUE", "$\\lambda$")

# obesity coefficient map
cmonames <- c(
  base_termnames, str_c("$\\gamma$: ", base_termnames[-1]), 
  "Physical Activity", "$\\gamma$: Physical Activity",
  rep("Accessibility", 3),
  "$\\lambda$: spatial correlation"
)
cmo <- as.list(cmonames)
names(cmo) <- c(names(obesity_models$Base$coefficients), 
                "euc_access", "euc_multi", "walk10TRUE",  "$\\lambda$")
```

\begin{table*}
  \caption{\label{tab:pa-fullmodels} Estimated Effect of Accessibility on Physical Activity Rates}
  \begin{center}
  \scalebox{0.8}{
```{r pa-fullmodels, results = "asis"}
texreg(
  pa_models, digits = 4, ci.force = TRUE,
  booktabs = TRUE, use.packages = FALSE, 
  custom.coef.map = cm,
  custom.model.names = c("No Access", "Size and Distance", "Amenities", "10-minute Walk"), 
  table = F,
  include.aic = F, include.lr = F,
  custom.note = "%stars 95\\% confidence interval in brackets.")
```
}\end{center}
\end{table*}

\begin{table*}
  \caption{\label{tab:ob-fullmodels} Estimated Effect of Accessibility on Obesity Rates}
  \begin{center}
  \scalebox{0.8}{
```{r ob-fullmodels, results="asis"}
texreg(
  obesity_models, digits = 4, ci.force = TRUE,
  booktabs = TRUE, use.packages = FALSE, 
  custom.coef.map = cmo,
  custom.model.names = c("No Access", "Size and Distance", "Amenities", "10-minute Walk"), 
  table = F,
  include.aic = F, include.lr = F,
  custom.note = "%stars 95\\% confidence interval in brackets.")
```
}\end{center}
\end{table*}
